Concurrent Programming in Harmony

### 2022-01-09 book/paper.tex

>>>>

\section{Formal Specification}
\label{ap:formal}

A formal specification of the Harmony Virtual Machine is underway but
not yet completed.
Given a Harmony program, you can output the TLA+ specification for
the program using the following command:

\begin{code}
\begin{verbatim}
$ harmony -o program.tla program.hny
\end{verbatim}
\end{code}

For many Harmony programs, such as Peterson's algorithm and the Dining
Philosophers in this book, the result is complete enough to run through
the TLC model checker.
